APMTH 221 Final Project Proposal

### 2018-02-21 reports/initial-proposal/initial-proposal.tex
Start working on future work
Suggest neural networks and optimization techniques

>>>>

We have the following tentative ideas which we may or may not individually
implement, but from which we will source our  work,

\begin{itemize}

\item We will use linear programs to calculate Wasserstein distances for
discrete metric spaces. We will explore average complexity for randomly
generated test cases.

\item Training a neural network to hot-start an optimization algorithm for the
discrete case.

\item Exploring other relevant optimization techniques such as simulated
annealing and genetic algorithms.

\end{itemize}
